---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(pkghw4ge)
```

You will need to load the following packages: **tidyverse** and in particular **stats**.

Description: More about what it does.
             The package contains and will load the functions created in Ex1.
             You will find so functions as: 'Bootstrap', 'plot.bootstrap', 
             'print.bootstrap','summary.bootstrap' and 'summary.bootstrap.mod'.
             The package contains various functions that will allow you to mainly
             use the a bootstrap    
             modification from the previous homework3.    
             The 'Bootstrap' function will provide you always an object of class
             bootstrap.  
             The 'print.bootstrap' function is a method of the basic print
             function. 
             The function will print information regarding the bootstrap class
             generated by the Bootstrap function.   
             The 'summary.bootstrap' function is a method of the basic summary
             function. 
             It will print a summary regarding the bootstrap class generated by
             the Bootstrap function. 
             The returned values will be of class summary.bootstrap.   
             The 'print.summary.bootstrap' function is a method of the basic
             print function. 
             It will print a summary regarding the summary.bootstrap class
             generated by the 'summary.bootstrap' function.   
             The 'plot.bootstrap' function is a method of the original 'plot'
             function made for the bootstrap class. 
             It will return a box-plot.
